Supplement for: Carbon cycling in mature and regrowth forests globally: a macroecological synthesis based on the global Forest Carbon (ForC) database

### 2020-09-29 manuscript/ERL_global_C_SI.Rmd
knit in new results, working on text

```{r eval = TRUE, echo=FALSE, warning=FALSE}
library(knitr)
library(kableExtra)
table_pt <- read.csv("tables_figures/SI_age_trend_model_summaries.csv", 
                     #colClasses=c("NULL", NA, NA, NA, NA), 
                     #col.names=c("NULL", "Parameter", "Estimate", "SE", "$t_{value}$"), 
                     stringsAsFactors = FALSE, check.names = FALSE)
kable(table_pt, format = "latex", booktabs = TRUE, longtable = TRUE,  escape = F, linesep = c('\\addlinespace'))%>%
  #pack_rows("NEP", 1, 5, latex_gap_space = "1em", colnum = 4, hline_before = FALSE) %>%
  #pack_rows("GPP", 6, 10, latex_gap_space = "1em", colnum = 4, hline_before = FALSE) %>%
  #pack_rows("NPP", 11, 15, latex_gap_space = "1em", colnum = 4, hline_before = FALSE) %>%
  #pack_rows("ANPP", 16, 23, latex_gap_space = "1em", colnum = 4, hline_before = FALSE) %>%
  #pack_rows("ANPP_woody", 24, 28, latex_gap_space = "1em", colnum = 4, hline_before = FALSE) %>%
  #pack_rows("ANPP_stem", 29, 36, latex_gap_space = "1em", colnum = 4, hline_before = FALSE) %>%
  #pack_rows("ANPP_branch", 37, 40, latex_gap_space = "1em", colnum = 4, hline_before = FALSE) %>%
  kable_styling(latex_options =c("repeat_header"), protect_latex = T, font_size = 7)
```

>>>>

```{r eval = TRUE, echo=FALSE, warning=FALSE}
library(knitr)
library(kableExtra)
table_pt <- read.csv("tables_figures/SI_age_trend_model_summaries.csv", 
                     #colClasses=c("NULL", NA, NA, NA, NA), 
                     #col.names=c("NULL", "Parameter", "Estimate", "SE", "$t_{value}$"), 
                     stringsAsFactors = FALSE, check.names = FALSE)
kable(table_pt, format = "latex", booktabs = TRUE, longtable = TRUE,  escape = F)%>%
  #pack_rows("NEP", 1, 5, latex_gap_space = "1em", colnum = 4, hline_before = FALSE) %>%
  #pack_rows("GPP", 6, 10, latex_gap_space = "1em", colnum = 4, hline_before = FALSE) %>%
  #pack_rows("NPP", 11, 15, latex_gap_space = "1em", colnum = 4, hline_before = FALSE) %>%
  #pack_rows("ANPP", 16, 23, latex_gap_space = "1em", colnum = 4, hline_before = FALSE) %>%
  #pack_rows("ANPP_woody", 24, 28, latex_gap_space = "1em", colnum = 4, hline_before = FALSE) %>%
  #pack_rows("ANPP_stem", 29, 36, latex_gap_space = "1em", colnum = 4, hline_before = FALSE) %>%
  #pack_rows("ANPP_branch", 37, 40, latex_gap_space = "1em", colnum = 4, hline_before = FALSE) %>%
  kable_styling(latex_options =c("repeat_header"), protect_latex = T, font_size = 7)
```

### 2020-09-29 manuscript/ERL_global_C_review.Rmd
knit in new results, working on text

- We're still finalizing the data (and adding some data). Outliers in plots will all be checked/ resolved, and we'll be able to pull in more data (*GROA* needs classification by dominant vegetation before it can be pulled in, and we're working on that)
- "**???**" indicates a reference that we have entered in the .Rmd file, but not yet in the bibliography file. Don't worry about those. (However, places with "REF" need references)
- bold/ italic text indicates places where I know we need to go back and revisit/ fill in info

@@

For variables with records from $\ge$ 7 distinct geographic areas, these ensemble C budgets were generally consistent.
*That is, component variables summed to within one standard deviation of their respective aggregate variables in all but* **two** *instances, both in temperate conifer forests (Fig. 5).* 
**(check all this with final results: https://github.com/forc-db/ForC/blob/master/numbers_and_facts/C_cycle_closure.csv, and be sure to write out variable names at first occurance, and provide a bit more detail) ** 
*For the temperate conifer biome, the average composite measure of aboveground biomass (Bag) was less than the combined average value of woody biomass (Bag-wood) and foliage biomass (Bfoliage), partly due to the very high estimates of Bag-wood.*
*Within this biome, $B_{ag}<B_{ag-wood}+B_{foliage}$ and $B_{root}<B_{root-coarse}+B_{root-fine}$ because $B_{ag-wood}$ and $B_{root-coarse}$ were very high, with strongly disproportionate numbers of records from the high-biomass forests of the US Pacific Northwest (Figs. S18, S21).*

>>>>

- "**???**" indicates a reference that we have entered in the .Rmd file, but not yet in the bibliography file. Don't worry about those. (However, places with "REF" need references)
- bold/ italic text indicates places where I know we need to go back and revisit/ fill in info

@@

For variables with records from $\ge$ 7 distinct geographic areas, these ensemble C budgets were generally consistent.
That is, component variables summed to within one standard deviation of their respective aggregate variables in all but one instance.
In the temperate conifer biome, the average composite measure of root biomass ($B_{root}$) was less than the combined average value of coarse and fine root biomass ($B_{root-coarse}$ and $B_{root-fine}$, respectively).
This lack of closure was driven by very high estimates of $B_{root-coarse}$ from high-biomass forests of the US Pacific Northwest.
